\huge Tor's Usability for Censorship Circumvention

### 2016-04-14 pets2017-paper/pets2017-paper.tex
Revise description of environments.

\subsection{Setup}
\label{sec:setup}
We simulated three censorship environments for our qualitative and quantitative user studies. \\

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Mild censorship (E1)}: 
(Representative of countries such as France and Australia.)
Certain domains are blocked. Reaching these 
domains requires a censorship circumvention 
tool like Tor, but Tor is not explicitly blocked. 
The default option to ``connect'' to the Tor network 
directly will circumvent this censor. Additional correct
bridge or proxy configurations are optional.

\item {\bfseries Intermediate censorship (E2)}: 
(Representative of countries such as Tunisia.)
Certain domains are blocked. Censorship circumvention
tools such as Tor are blocked. Since all public Tor
relay nodes are blocked, the default option to ``connect'' to the Tor network
directly will fail. Any choice of a hard-coded bridge
or a valid non-public bridge will circumvent this censor.  
Additional correct proxy configuration is optional.

\item {\bfseries Comprehensive censorship (E3)}:
(Representative of countries such as China and Syria.)
Certain domains are blocked. Censorship circumvention tools
are thoroughly blocked. Tor is blocked by blocking all public
Tor relay nodes, and the censor has examined source code to block
all hard-coded bridge relays in the configuration interface. The default option
to ``connect'' to the Tor network directly will fail. Most bridges will fail,
but ``meek-amazon,'' ``meek-azure,'' and ``meek-google'' still work.
This is because domain-fronting requires censors to block entire CDNs to also
block this transport, which causes huge collateral blocking damage that
makes the censorship very visible and inconvenient. Currently, even
aggressive censorship environments resistant blocking entire CDNs.
(See~\cite{fifield2015blocking} for additional details.)
\end{itemize}

These reproducible, stable environments are informed by our experience 
with pluggable transports and knowledge of commonly seen censorship 
techniques. Their goal in our user study is not to replicate the network 
environment in any particular country, but to require our distinct configurations
so that interface paths are tested.

\begin{table}
\centering
\begin{tabular}{r c c c}
& E1 & E2 & E3 \\
% \noalign{\hrule}
websites blocked & X & X & X \\
public relays blocked & & X & X \\
default bridges blocked & & & X \\
\end{tabular}
\caption{
Summary of our simulated censorship environments.
E1 only requires participants to click ``Connect'';
E2 requires selection of an included bridge;
and E3 requires selection of a specific included bridge,
or manual configuration of a custom bridge.
E2's blocking is a superset of E1's;
similarly E3's is a superset of E2's.
}
\label{tab:environments}
\end{table}

@@

\subsubsection{Setup}
We simulated the same three censorship environments from 
our qualitative user study. Details of the mild, intermediate, and advanced 
censorship environments and what configurations are necessary for a 
successful connection can be found in Section~\ref{sec:setup}.

>>>>

\subsection{Censorship Environments}
\label{sec:environments}
We simulated three censorship environments,
which we labeled ``E1,'' ``E2,'' and ``E3''
in order of increasing severity.
We designed the environments to be representative
of what, in our estimation, are important real-world
cases of censorship, but they are not intended to imitate
any particular country's censorship exactly.

\smallskip

\begin{description}
\item[E1: Mild censorship]
The E1 environment only blocks some websites,
as if by DNS poisoning.
We blocked subdomains of torproject.org
and wikipedia.org.
(Reading a page on en.wikipedia.org was the participants' main goal.)
To succeed in this environment,
participants had only to click ``Connect'' on the first screen;
additional configuration was possible but unnecessary.
% (Representative of countries such as France and Australia.)

\item[E2: Intermediate censorship]
The E2 environment blocks websites as in E1;
and additionally blocks the IP addresses of public Tor relays
and directory authorities, simulating a censor that knows
about circumvention and tries to stop it.
In this environment, simply clicking ``Connect'' will not work;
participants had at least to select a built-in bridge
(any type other than ``flashproxy'' would work).
A custom bridge would work but was not necessary.
% (Representative of countries such as Tunisia.)

\item[E3: Comprehensive censorship]
The E3 environment blocks websites and Tor relays as in E1 and E2;
and additionally blocks the built-in default bridge IP addresses
found in the Tor Browser source code.
To succeed in this environment, participants had either to select
one of the ``meek'' built-in bridges (no other type would work),
or to acquire their own custom bridge and enter it manually.
% (Representative of countries such as China and Syria.)
\end{description}

\smallskip

Table~\ref{tab:environments} summarizes what is blocked
in each environment.
We used features of the Windows operating system to implement
the above environments.
To simulate website blocking, we added entries to the hosts file,
mapping domain names to the address 127.0.0.1.
For IP address blocking, we used Windows Firewall rules.

\begin{table}
\centering
\begin{tabular}{r c c c}
& E1 & E2 & E3 \\
% \noalign{\hrule}
websites blocked & X & X & X \\
public relays blocked & & X & X \\
default bridges blocked & & & X \\
\end{tabular}
\caption{
Summary of our simulated censorship environments.
E1 only requires participants to click ``Connect'';
E2 requires selection of a built-in bridge;
and E3 requires selection of a specific type of built-in bridge,
or manual configuration of a custom bridge.
E2's blocking is a superset of E1's;
similarly E3's is a superset of E2's.
}
\label{tab:environments}
\end{table}

@@

\subsubsection{Setup}
We simulated the same three censorship environments from 
our qualitative user study. Details of the mild, intermediate, and advanced 
censorship environments and what configurations are necessary for a 
successful connection can be found in Section~\ref{sec:environments}.
